---
title: "Modeling Buildi Up - Child Fosterage"
author: "Maya, Brady, & Tommy"
date: 'Spring 2023'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the required packages
```{r message = FALSE, warning = FALSE}
library(haven)
library(tidyr)
library(readr)
library(dplyr)
library(stringr)
library(ggplot2)
library(lattice)
library(lme4)
library(tidyverse)
library(stringr)
library(lmerTest)
library(cAIC4)
library(MuMIn)
library(parallel)
library(glmmLasso)
```

# Load the raw data from DHS
```{r}
# Read in the data
Training <- read_csv("Clean_Data_Training.csv")
Training_NA <- na.omit(Training)

Testing <- read_csv("Clean_Data_Testing.csv")
Testing_NA <- na.omit(Testing)
```

# Forward Stepwise Model(Adding the 1st variable)
```{r}
col_name <- c("age_child", "first_born", "sex_child", "marital_status", "union_status", "non_union_status", "edu_level_mother", "num_trips", "owner_house", "wealth_index", "traveled_12", "partners_education", "currently_working", "literacy", "current_age_respondent", "type_dejure_residence", "age_first_sex", "worked_12")

cores <- detectCores()
cl <- makeCluster(cores)

# Export necessary variables to the worker processes

clusterExport(cl, c("col_name"))
clusterExport(cl, c("Training_NA"))
clusterEvalQ(cl, library(lme4))
clusterEvalQ(cl, c(library(MuMIn)))

# Define a function to fit the model and return AIC
fit_model <- function(x) {
  formula <- formula(paste0("child_foster ~ 1 + ", x, " + (1 | mother_id)"))
  model <- glmer(formula, data = Training_NA, family = binomial)
  AIC(model)
}

# Use parLapply to fit models for each predictor in parallel
aic_values <- unlist(parLapply(cl, col_name, fit_model))

# Stop the cluster
stopCluster(cl)

# Output the results
aic_values
```

# Forward Stepwise Model(Adding the 2nd variable)
```{r}
col_name <- c("first_born", "sex_child", "marital_status", "union_status", "non_union_status", "edu_level_mother", "num_trips", "owner_house", "wealth_index", "traveled_12", "partners_education", "currently_working", "literacy", "current_age_respondent", "type_dejure_residence", "age_first_sex", "worked_12")

cores <- detectCores()
cl <- makeCluster(cores)

# Export necessary variables to the worker processes

clusterExport(cl, c("col_name"))
clusterExport(cl, c("Training_NA"))
clusterEvalQ(cl, library(lme4))
clusterEvalQ(cl, c(library(MuMIn)))

# Define a function to fit the model and return AIC
fit_model <- function(x) {
  formula <- formula(paste0("child_foster ~ 1 + age_child + ", x, " + (1 | mother_id)"))
  model <- glmer(formula, data = Training_NA, family = binomial)
  AIC(model)
}

# Use parLapply to fit models for each predictor in parallel
aic_values <- unlist(parLapply(cl, col_name, fit_model))

# Stop the cluster
stopCluster(cl)

# Output the results
aic_values
```

# Forward Stepwise Model(Adding the 3rd variable)
```{r}
col_name <- c("first_born", "sex_child", "marital_status", "union_status", "non_union_status", "edu_level_mother", "num_trips", "owner_house", "wealth_index", "traveled_12", "partners_education", "currently_working", "literacy", "type_dejure_residence", "age_first_sex", "worked_12")

cores <- detectCores()
cl <- makeCluster(cores)

# Export necessary variables to the worker processes

clusterExport(cl, c("col_name"))
clusterExport(cl, c("Training_NA"))
clusterEvalQ(cl, library(lme4))
clusterEvalQ(cl, c(library(MuMIn)))

# Define a function to fit the model and return AIC
fit_model <- function(x) {
  formula <- formula(paste0("child_foster ~ 1 + age_child + current_age_respondent + ", x, " + (1 | mother_id)"))
  model <- glmer(formula, data = Training_NA, family = binomial)
  AIC(model)
}

# Use parLapply to fit models for each predictor in parallel
aic_values <- unlist(parLapply(cl, col_name, fit_model))

# Stop the cluster
stopCluster(cl)

# Output the results
aic_values
```

# Forward Stepwise Model(Adding the 4th variable)
```{r}
col_name <- c("first_born", "sex_child", "marital_status", "union_status", "edu_level_mother", "num_trips", "owner_house", "wealth_index", "traveled_12", "partners_education", "currently_working", "literacy", "type_dejure_residence", "age_first_sex", "worked_12")

cores <- detectCores()
cl <- makeCluster(cores)

# Export necessary variables to the worker processes

clusterExport(cl, c("col_name"))
clusterExport(cl, c("Training_NA"))
clusterEvalQ(cl, library(lme4))
clusterEvalQ(cl, c(library(MuMIn)))

# Define a function to fit the model and return AIC
fit_model <- function(x) {
  formula <- formula(paste0("child_foster ~ 1 + age_child + current_age_respondent + non_union_status + ", x, " + (1 | mother_id)"))
  model <- glmer(formula, data = Training_NA, family = binomial)
  AIC(model)
}

# Use parLapply to fit models for each predictor in parallel
aic_values <- unlist(parLapply(cl, col_name, fit_model))

# Stop the cluster
stopCluster(cl)

# Output the results
aic_values
```

# Forward Stepwise Model(Adding the 5th variable)
```{r}
col_name <- c("sex_child", "marital_status", "union_status", "edu_level_mother", "num_trips", "owner_house", "wealth_index", "traveled_12", "partners_education", "currently_working", "literacy", "type_dejure_residence", "age_first_sex", "worked_12")

cores <- detectCores()
cl <- makeCluster(cores)

# Export necessary variables to the worker processes

clusterExport(cl, c("col_name"))
clusterExport(cl, c("Training_NA"))
clusterEvalQ(cl, library(lme4))
clusterEvalQ(cl, c(library(MuMIn)))

# Define a function to fit the model and return AIC
fit_model <- function(x) {
  formula <- formula(paste0("child_foster ~ 1 + age_child + current_age_respondent + non_union_status + first_born + ", x, " + (1 | mother_id)"))
  model <- glmer(formula, data = Training_NA, family = binomial)
  AIC(model)
}

# Use parLapply to fit models for each predictor in parallel
aic_values <- unlist(parLapply(cl, col_name, fit_model))

# Stop the cluster
stopCluster(cl)

# Output the results
aic_values
```

# Forward Stepwise Model(Adding the 6th variable)
```{r}
col_name <- c("sex_child", "marital_status", "union_status", "edu_level_mother", "num_trips", "owner_house", "traveled_12", "partners_education", "currently_working", "literacy", "type_dejure_residence", "age_first_sex", "worked_12")

cores <- detectCores()
cl <- makeCluster(cores)

# Export necessary variables to the worker processes

clusterExport(cl, c("col_name"))
clusterExport(cl, c("Training_NA"))
clusterEvalQ(cl, library(lme4))
clusterEvalQ(cl, c(library(MuMIn)))

# Define a function to fit the model and return AIC
fit_model <- function(x) {
  formula <- formula(paste0("child_foster ~ 1 + age_child + current_age_respondent + non_union_status + first_born + wealth_index + ", x, " + (1 | mother_id)"))
  model <- glmer(formula, data = Training_NA, family = binomial)
  AIC(model)
}

# Use parLapply to fit models for each predictor in parallel
aic_values <- unlist(parLapply(cl, col_name, fit_model))

# Stop the cluster
stopCluster(cl)

# Output the results
aic_values
```

# Forward Stepwise Model(Adding the 7th variable)
```{r}
col_name <- c("sex_child", "marital_status", "union_status", "num_trips", "owner_house", "traveled_12", "partners_education", "currently_working", "literacy", "type_dejure_residence", "age_first_sex", "worked_12")

cores <- detectCores()
cl <- makeCluster(cores)

# Export necessary variables to the worker processes

clusterExport(cl, c("col_name"))
clusterExport(cl, c("Training_NA"))
clusterEvalQ(cl, library(lme4))
clusterEvalQ(cl, c(library(MuMIn)))

# Define a function to fit the model and return AIC
fit_model <- function(x) {
  formula <- formula(paste0("child_foster ~ 1 + age_child + current_age_respondent + non_union_status + first_born + wealth_index + edu_level_mother + ", x, " + (1 | mother_id)"))
  model <- glmer(formula, data = Training_NA, family = binomial)
  AIC(model)
}

# Use parLapply to fit models for each predictor in parallel
aic_values <- unlist(parLapply(cl, col_name, fit_model))

# Stop the cluster
stopCluster(cl)

# Output the results
aic_values
```

# Forward Stepwise Model(Adding the 8th variable)
```{r}
col_name <- c("sex_child", "marital_status", "union_status", "num_trips", "owner_house", "partners_education", "currently_working", "literacy", "type_dejure_residence", "age_first_sex", "worked_12")

cores <- detectCores()
cl <- makeCluster(cores)

# Export necessary variables to the worker processes

clusterExport(cl, c("col_name"))
clusterExport(cl, c("Training_NA"))
clusterEvalQ(cl, library(lme4))
clusterEvalQ(cl, c(library(MuMIn)))

# Define a function to fit the model and return AIC
fit_model <- function(x) {
  formula <- formula(paste0("child_foster ~ 1 + age_child + current_age_respondent + non_union_status + first_born + wealth_index + edu_level_mother + traveled_12 + ", x, " + (1 | mother_id)"))
  model <- glmer(formula, data = Training_NA, family = binomial)
  AIC(model)
}

# Use parLapply to fit models for each predictor in parallel
aic_values <- unlist(parLapply(cl, col_name, fit_model))

# Stop the cluster
stopCluster(cl)

# Output the results
aic_values
```

# Get the initial forward model
```{r}
initial_forward_model <- glmer(child_foster ~ age_child + first_born + sex_child + marital_status + union_status + non_union_status + age_cohabitation + edu_level_mother + num_trips + owner_house + wealth_index + traveled_12 + partners_education + currently_working + literacy + current_age_respondent + type_dejure_residence + age_first_sex + worked_12 + (1 | mother_id), data = Training_NA, family = binomial)
```

# Get the final forward model
```{r}
final_forward_model <- glmer(child_foster ~ age_child + first_born + non_union_status + wealth_index + edu_level_mother + current_age_respondent + (1 | mother_id), data = Training_NA, family = binomial)
```



