---
title: "Model Visualizations - Child Fosterage"
author: "Maya, Brady, & Tommy"
date: 'Spring 2023'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the required packages
```{r message = FALSE, warning = FALSE}
library(haven)
library(tidyr)
library(readr)
library(dplyr)
library(stringr)
library(ggplot2)
library(lattice)
library(lme4)
library(tidyverse)
library(stringr)
library(lmerTest)
library(cAIC4)
library(MuMIn)
library(parallel)
library(glmmLasso)
library(cvms)
library(emmeans)
library(numDeriv)
library(RCurl)
library(reshape2)
library(plyr)
library(RColorBrewer)
library(emmeans)
library(influence.ME)
```

# Load the cleaned data
```{r, warning = FALSE}
# Read in the data
Training <- read_csv("Clean_Data_Training.csv")
Training_NA <- na.omit(Training)

Testing <- read_csv("Clean_Data_Testing.csv")
Testing_NA <- na.omit(Testing)

Training_NAs <- Training_NA
Testing_NAs <- Testing_NA

```

# Load the raw data from DHS
```{r, warning = FALSE}
# create the final forward selection model with 6 variables
final_model <- glmer(child_foster ~ age_child + current_age_respondent + num_union_status + first_born + wealth_index + edu_level_mother + (1 | mother_id), data = Training_NA, family = binomial)
```

# Listing all categorical combinations
```{r}
first_born_categories <- unique(Training_NA$first_born)
num_union_status_categories <- unique(Training_NA$num_union_status)
wealth_index_categories <- unique(Training_NA$wealth_index)
education_categories <- unique(Training_NA$edu_level_mother)

categorical_grid <- expand.grid(first_born = first_born_categories,
                                num_union_status = num_union_status_categories,
                                wealth_index = wealth_index_categories, 
                                education_level = education_categories,
                                number_of_instances = 0)
print(categorical_grid)

in_data_count <- rep(0, nrow(categorical_grid))
for(x in 1:nrow(categorical_grid)){
  in_data_count[x] <- sum(Training_NA$first_born == categorical_grid[x,1] & 
                          Training_NA$num_union_status == categorical_grid[x,2] &
                          Training_NA$wealth_index == categorical_grid[x,3] &
                          Training_NA$edu_level_mother == categorical_grid[x,4], 
                          na.rm = TRUE)
  categorical_grid[x, 5] = in_data_count[x]
}
```


## Counting frequency of cases within each factor level combination
```{r}
in_data_count <- rep(0, nrow(categorical_grid))
for (x in 1:nrow(categorical_grid)){
  in_data_count[x] <- sum(Training_NA$first_born == categorical_grid[x, 1] & Training_NA$num_union_status == categorical_grid[x, 2] & Training_NA$wealth_index == categorical_grid[x, 3] & Training_NA$edu_level_mother == categorical_grid[x, 4], na.rm = TRUE)
}
print(categorical_grid)
```

# Visualization for the odds ratio
```{r}
# Estimates of fixed effects, 95% confidence intervals, odds ratios, and odds ratio confidence intervals 
fixed_effects <- fixef(final_model)
se_effects <- se.fixef(final_model)
LB_est <- fixed_effects-(se_effects*1.96)
UB_est <- fixed_effects+(se_effects*1.96)
odds_ratio_effects <- exp(fixed_effects)
LB_odds <- odds_ratio_effects-(se_effects*1.96)
UB_odds <- odds_ratio_effects+(se_effects*1.96)

# Create a table with these estimates
est_table <- data.frame(
  fixed_effects = fixed_effects,
  LB_est = LB_est,
  UB_est = UB_est,
  odds_ratio_effects = odds_ratio_effects,
  LB_odds = LB_odds,
  UB_odds = UB_odds
)
est_table <- est_table[2:7, ]

variable_name <- c("age_child", "current_age_respondent", "num_union_status", "first_born", "wealth_index", "edu_level_mother")
fixed_effects_visualization <- ggplot(est_table, aes(y = variable_name, x = fixed_effects, xmin = LB_est, xmax = UB_est)) + geom_pointrange() + ylab("Selected Variables") + xlab("Fixed Effects")
odds_visualization <- ggplot(est_table, aes(y = variable_name, x = odds_ratio_effects, xmin = LB_odds, xmax = UB_odds)) + geom_pointrange() + ylab("selected Variables") + xlab("Odds Ratio")
```

# Analysis of Variance Table
```{r}
# Determining significance of each variable in the final model 
# Removing age_child
model_ac <- glmer(child_foster ~  current_age_respondent + num_union_status + first_born + wealth_index + edu_level_mother + (1 | mother_id), data = Training_NA, family = binomial)
anova(model_ac, final_model)
# Removing current_age_respondent
model_car <- glmer(child_foster ~   age_child + num_union_status + first_born + wealth_index + edu_level_mother + (1 | mother_id), data = Training_NA, family = binomial)
anova(model_car, final_model)
# Removing num_union_status
model_nus <- glmer(child_foster ~  current_age_respondent + age_child + first_born + wealth_index + edu_level_mother + (1 | mother_id), data = Training_NA, family = binomial)
anova(model_nus, final_model)
# Removing first_born
model_fb <- glmer(child_foster ~  current_age_respondent + num_union_status + age_child + wealth_index + edu_level_mother + (1 | mother_id), data = Training_NA, family = binomial)
anova(model_fb, final_model)
# Removing wealth_index
model_wi <- glmer(child_foster ~  current_age_respondent + num_union_status + first_born + age_child + edu_level_mother + (1 | mother_id), data = Training_NA, family = binomial)
anova(model_wi, final_model)
# Removing edu_level_mother
model_elm <- glmer(child_foster ~  current_age_respondent + num_union_status + first_born + wealth_index + age_child + (1 | mother_id), data = Training_NA, family = binomial)
anova(model_elm, final_model)
```

## Ignore the following codes, not part of final deliverable
## Below is Psuedo-code, it does not model the current model and is included in the code as a work in progress for potential future use, for creating predicted probability and confidence intervals for each factor-level combination 

# Making numeric variables categorical
```{r, eval=FALSE}
hist(Training_NA$age_child)
mean(Training_NA$age_child)
Training_NA$cat_age_child <- ifelse(Training_NA$age_child <= 7.9, "young", "old")

hist(Training_NA$current_age_respondent)
mean(Training_NA$current_age_respondent)
Training_NA$cat_age_resp <- ifelse(Training_NA$current_age_respondent <= 32.3, "young", "old")
```

## CALCULATING THE PREDICTED PROBABILITY AND CONFIDENCE INTERVALS FOR EACH FACTOR-LEVEL COMBINATION
```{r, eval=FALSE}
f_model_6 <- glmer(child_foster ~ age_child + current_age_respondent + num_union_status + first_born + wealth_index + edu_level_mother + (1 | mother_id), data = Training_NA, family = binomial)

# Calculating estimated marginal means
em = emmeans(f_model_6, ~ age_child + current_age_respondent + num_union_status + first_born + wealth_index + edu_level_mother)

# Extracting predicted values
emdf = summary(em, by = c("num_union_status", "first_born", "wealth_index", "education_level_mother"), type = "response")
```

## ASSEMBLING TABLE WITH (1) FACTOR-LEVEL COMBINATIONS, (2) PROBABILITIES AND CONFIDENCE INTERVALS, AND (3) FREQUENCY OF CASES   
```{r, eval=FALSE}
# Adding probability to factor-level combination grid
categorical_grid$predicted_prob <- emdf$prob

# Adding lower and upper confidence interval values to factor-level combination grid
categorical_grid$LCL <- emdf$asymp.LCL
categorical_grid$UCL <- emdf$asymp.UCL

# Adding frequency of cases to factor-level combination grid
categorical_grid$count_in_dataset <- in_data_count

# Sort categorical_grid by descending order of frequency of cases
categorical_grid <- categorical_grid[order(-categorical_grid$count_in_dataset), ]

# Printing categorical_grid
categorical_grid 
```

# CREATING PROBABILITY AND CONFIDENCE INTERVAL VISUALIZATIONS
```{r, eval=FALSE}
# Loading ggplot package 
library(ggplot2)

# Using the categorical_grid data frame to create a bar plot of probability with confidence intervals (arranged by descending order of probability)
ggplot(categorical_grid, aes(x = reorder(paste0("FirstBorn: ", first_born, "\nUnionStatus: ", num_union_status, "\nWealth: ", wealth_index, "\nEducationStatus:", edu_level_mother), -predicted_prob), y = predicted_prob)) +
  geom_bar(stat = "identity", fill = "#4C78A8", position = position_dodge(width = 1)) +
  geom_errorbar(aes(ymin = LCL, ymax = UCL), width = 0.2, position = position_dodge(width = 1)) +
  xlab("") +
  ylab("Predicted Probability") +
  ggtitle("Predicted Probability by Variable Combination including UCL and LCL as error bars") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

